---
title: "Lab2 - Deepak and Rattanan"
output: html_notebook
---

### We would like to convery two stories <br> 
<ul> 
  <li> How consumption of music has been changed throughout the years </li>
  <li> <span style = 'color:blue'> Top 10 songs </span> that have the highest instance impact </li>
</ul> 


Importing the libraries and the CSV File

```{r}
library(tidyverse)
library(tsibble)
library(lubridate)
```
```{r}
data <- read_csv("Hot100.csv")
```

```{r}
data
```


---
The number of songs has been on the chart consecutively for 5 weeks or more over a time series of data


##Filtering out the data set and creating a year column


```{r}
consecutive_data <- data |> filter(time_on_chart >= 10) |> distinct(song_id , .keep_all = TRUE)
```

Pre-viewing the cleaned data
```{r}
consecutive_data
```

Getting the chart year of these songs

```{r}
year <- year(consecutive_data |> pull(chart_date))
```

Adding the column year to the updated dataset
```{r}
consecutive_data <- consecutive_data |> mutate(year = year) |> relocate(year)
consecutive_data
```

Getting the number of unique songs per year and removed the outlier of year 2023
```{r}
songs_per_year <- consecutive_data |> 
  group_by(year) |>
  summarize(songs = n_distinct(song_id)) |> filter(year != 2023)
```

```{r}
songs_per_year
```


### Plot - Number of Songs vs Year

```{r}
ggplot(data = songs_per_year, aes(x = year, y = songs)) +
  geom_line(color = "red") +
  labs(x = "Year", y = "Number of songs",
       title = "Number of unique songs on the Hot 100 chart by year")
```

## Instance impact 
Get the top 10 instance values of all time
```{r}
instance_data <- data |> group_by(song_id) |> top_n(1,instance) |> distinct(song_id, .keep_all = TRUE) |> arrange(desc(instance))
instance_data
```

Getting the top 10 rows of the tibble
```{r}
top_instance_data <- instance_data[1:10,]
top_instance_data
```


Top 10 songs with the highest number of repeated appearances on the chart

```{r}
ggplot(data = top_instance_data, aes(x = song, y = instance)) +
  geom_bar(stat = "identity", fill = "blue") +
  coord_flip() +
  labs(x = "Song", y = "Instances",
       title = "Top 10 songs with the highest number of repeated appearances on the chart")
```

Getting the song name as a list
```{r}
song_list <- as.list(top_instance_data$song)
song_list

```

We go throught the original dataset, and get all of the rows where the song is in the list
```{r}
song_data <- data |> filter(song %in% song_list)
song_data
```

Creating and adding month to this dataset
```{r}
month <- month(song_data |> pull(chart_date))
song_data <- song_data |> mutate(month = month) |> relocate(month)
song_data

```

## Facets of the popular songs

We know that most of the songs that has a recurring fan base is because they are Christmas songs, and they are being played during the time of Christmas. We can cross check this by looking at a facet of these songs


```{r}
ggplot(data = song_data, aes(x = month, y=chart_position)) + geom_point(size = 2, color = "green") + scale_x_continuous(breaks = seq(0,13,1)) + facet_wrap(~song) + theme(strip.text = element_text(
    size = 7, color = "brown"), axis.text.x = element_text(angle = 0, size = 7))

```




